MCTS Applied to Co-operative Problems

### 2015-08-06 Report/response.tex

\documentclass{article}
\title{Response}

\begin{document}
\maketitle
\section{Response to the reviewers}
Dear Reviewers,

Please find below our responses to your comments.

We would like to thank the reviewers for their insightful comments, that have truly enabled us to make many improvements to this paper. We hope you will agree that the paper has matured into a quality that allows for publication.

@@

Yours sincerely,

The Authors.

\subsection{Review 1 (Reviewer A)}
\paragraph*{\textit{Introduction: The introduction is well written but oddly doesn't contain discussion about cooperative games. The introduction starts by discussing general game playing (which is not a main topic of the paper) and then presents MCTS (which is) but the discussion of cooperative games is missing.}}
Added section on co-operative games.

``Games that feature co-operation of some form between human players and AI agents are commonplace. Most however feature very limited forms of co-operation that are typically scripted such as in most FPS games. Typically FPS games give the mere impression of co-operation, though any player that looks carefully at it will see the tell tale signs of scripting. Where FPS games typically excel at co-operation is in online modes that enable teams of humans to play against each other. Some games even provide squad structures and communication allowing direct command for the purpose of better co-ordination as in Battlefield 2142 \cite{battlefield2142}. RTS games also often have a small number of features designed to facilitate communication in a bid to facilitate co-operation. Two games that stand out for co-operation are Microsoft's Rise of Nations \cite{riseofnations} and Mad Doc Software's Empire Earth 2 \cite{empireEarth2}. Rise of Nations allowed a human and AI player to operate the same set of units and buildings, though no communication was possible at all. This allowed a form of co-operation but the AI operated to its own agenda. Empire Earth 2 allowed for humans and AI agents to co-operate by letting plans be drawn up between them that could also be followed by both the human and AI agent. These allowed a fairly complex set of instructions to be created, despite the simple interface.

A highly popular game that had an entire mode designed for co-operation between humans was Valve's Portal 2 \cite{portal2}. This featured human sized lab test mazes with elements that required players to work together by activating buttons, moving cubes and using intra-dimensional portals to get to the end goal. Both players were required to reach the goal in order to complete the level.''

@@

``\emph{Doors -} Doors can either be open or closed. When open, the door is passable. When closed, the door is impassable. Doors are open whilst an \emph{Agent} is activating a linked \emph{Button}. If the \emph{Agent} stops activating the \emph{Button} the \emph{Door} will close.''
\paragraph*{\textit{Since 'Agents' are described as dark yellow, and since there are only two shades of yellow used, it would be wiser to describe a 'Goal' as rendered in bright yellow.}}
We have reworded the definition of \emph{Goal} to better describe the colour in relation to \emph{Agents}.

``\emph{Agents -} Agents are the moving objects that can activate buttons and the goal. \emph{Agents} are rendered in dark Yellow''
\paragraph*{\textit{the sentence "Agent 1 reached an item like this -Agent 2 would seemingly gain some purpose and typically head for the other items." is poorly worded and not very informative. It is better explained in the sentences below. Either remove this sentence or reword it.}}
Removed.

\paragraph*{\textit{it would be a good idea to give the maps meaningful names.}}
This has been done.

``\begin{itemize}
\item{\emph{SingleDoor} This map is a basic map with two rooms, single door and a button either side.}
\item{\emph{Pathfinding} This map is the same as level1.txt but without the \emph{Doors} and \emph{Buttons}. This was to test the \emph{Agent's} ability to solve the simplest problem.}
\item{\emph{SymmetricSingleDoor} This map was a modification of the level1.txt - making the map more symmetric and the action parts closer together.}
\item{\emph{ExtendedSide} This map was an extension of level1.txt with a second \emph{Goal} and some extra walls in the game. Spreading the action parts away from the door and buttons was the main purpose of this one}
\item{\emph{SideBySide} This map was a modification of level1.txt - putting a second \emph{Goal} in and making the map partly mirrored. Each \emph{Agent} began in a separate room to each other instead of together.}
\item{\emph{Airlock} This map was a new map, designed to give wildly different roles to each AI - the top Agent would have to travel through two doors (Like an airlock) that the bottom agent had access to the linked \emph{Buttons}. Then the top \emph{Agent} could collect the reward and allow the bottom \emph{Agent} access to the \emph{Goal}.}
\item{\emph{Butterfly} This map was a new map - with two rooms each with a \emph{Goal} and a door. This was designed to force each \emph{Agent} to be let into the \emph{Goal} room, and out of it again.}
\end{itemize}''

@@

\subsection{Review 2 (Reviewer D)}
\paragraph*{\textit{The writing is generally good, I only noticed one actual error "GGP[3]", but the tone is casual and a lot of inappropriately subjective comments are made}}
Have placed a space between GGP and the reference.
\paragraph*{\textit{The authors make a few dubious claims in the Introduction. GGP is not exactly "the field of writing Artificial Intelligence (AI) agents", and it is wrong to say that "MCTS doesn't requuire any knowledge about the game itself in order to play", as it needs to know starting position, legal moves, terminal states, etc. Perhaps the authors means "strategic knowledge". }}
Have clarified the definition of GGP and the terminology used to define MCTS's use of knowledge.

``GGP is the field of writing AI agents that can play a multitude of games without being written specifically for each one individually \cite{genesereth2005general}.''

``Standard MCTS plays best when it is able to search far enough to locate states that provide a reward. MCTS tends to stumble when the time or search depth limit given to it isn't sufficient to allow it to locate any sequence of actions that provides a reward in order to differentiate the root's children \cite{perez2012monte}. When MCTS can't find any single state that contained a reward, all children of the node will contain identical values and the algorithm will be forced to make a random choice.''
\paragraph*{\textit{The authors claim that MCTS works best when it is given rewards frequently. What is the evidence for this claim?}}
Have rewritten this to point out that MCTS can't provide anything but random if it isn't given enough time or depth to search to a state that provides a reward.

@@

``Standard MCTS plays best when it is able to search far enough to locate states that provide a reward. MCTS tends to stumble when the time or search depth limit given to it isn't sufficient to allow it to locate any sequence of actions that provides a reward in order to differentiate the root's children \cite{perez2012monte}. When MCTS can't find any single state that contained a reward, all children of the node will contain identical values and the algorithm will be forced to make a random choice.''
\paragraph*{\textit{The research problem is stated, but should be stated more clearly in the Introduction.}}
Added at the beginning of the introduction a clear statement of the research problem.

``This research problem that this paper will asses is how GGP agents perform when trying to solve a simple co-operative problem, with a focus on MCTS.''
\paragraph*{\textit{"MCTS can charge off achieving its own goals": it seems odd to describe an algorithm as "charging off".}}
Reworded.

``Unlike other domains where MCTS can solve tasks at its own pace and by itself ...''
\paragraph*{\textit{"This proves that the challenge...": no it doesn't, it indicates it.}}
Reworded to indicates.

``This indicates that the challenge of the task is high ...''
\paragraph*{\textit{"The shockingly good results...": too casual and subjective, overstating the case.}}
Reworded.

@@

``All \emph{Agents} are aware of the current score achieved, and therefore can calculate if a \emph{Goal} is reached.''

\paragraph*{\textit{In what sense this domain interesting compared to other domains?}}
We feel that this problem domain is interesting due to placing each agent that is typically designed to solve problems by themselves in an environment where they must rely on another agent performing certain sequences of actions. To quote the words of Reviewer F ``\textit{This proves to be an interesting reward space to explore, given that we are dealing with circumstances where players need to take action then await the outcome courtesy of another player}''. The domain also gains an interesting aspect when we consider the ability to, in a slowed down pace, allow human players to potentially communicate with a more advanced AI in order to improve performance in the domain. Communication within computer games is something that we believe would improve the feelings of immersion that the player feels.

\paragraph*{\textit{Is there a time limit for solving the problem? I think, if given infinite time, random agent can always solve level1 and the average score should be 1.0.
When and how do agents fail to solve a problem?}}
The time limit for the problem was 2,000 ticks. Given infinite time, random agent can always solve any level. Some experiments (100,000 runs per level) showed a pair of random agents took on average this many ticks to complete each level:

\begin{tabular}{|l|l|c|}
\hline
\textbf{Old Map Name} & \textbf{New Map Name} & \textbf{Avg Ticks to complete} \\
\hline
level1.txt & SingleDoor & 7250\\
\hline
level1E.txt & Pathfinder & 419\\
\hline
level2.txt & SymmetricSingleDoor & 7353\\
\hline
level3.txt & ExtendedSide& 13416\\
\hline
level4.txt & SideBySide & 7302\\
\hline
level5.txt & Airlock & 12469\\
\hline
level6.txt & Butterfly & 10246\\
\hline
\end{tabular}

These times are far too long for real time environment (40ms per tick gives an average solution time of nearly 7 minutes for Butterfly)

@@

``\emph{Walls -} Walls are impassable, and are fixed in position. \emph{Walls} are rendered in Black.''
\subsection{Review 4 (Reviewer B)}
\paragraph*{\textit{there is some mixup with agents being labeled 0 and 1 in the figures, but 1 and 2 in the text.}}
That section has been removed due to another comment that we received and so the mixup is gone.

\paragraph*{\textit{I did not understand the terms "UCT border" and "rollout border". Explain them. Are they related to "Max UCT" and "Max Rollout" in Fig. 2 ?}}
Both have been reworded to a more used set of terminology. The reworded section is shown above in R3's comments.
\paragraph*{\textit{What does 1+1 ES mean?}}
The paper has been expanded to include a brief description of the 1+1 ES technique.
\paragraph*{\textit{I did not quite understand how your MCTS works with multiple agents. Are you running independent simulations for each agent (I assume yes but it was not clear)? }}
Yes, each agent was running independent simulations. It has been made clearer in the paper that none of the agents have the ability to communicate with another agent, and that each agent is controlled by a single controller.

``None of the agents have the ability to communicate with another agent and each agent has a single controller.''
\paragraph*{\textit{I would like to see results for mixed agent teams.}}
Figures 6 and 7 have been retitled to better show that they were results for mixed agent teams.
\paragraph*{\textit{The issue of communication, especially learning communication, is very important and I suggest you focus on this for future research.}}
Have expanded the section in future work on communication to better reflect this.

``More work can be conducted in the writing of AI's to use communication in order to complete these challenges better amongst themselves. A framework for communication would be devised - with the requirement for fairly GGP like restrictions in mind. Use of the communication framework would need to likely be learned by the \emph{Agents} during play, posing a particular challenge for the future.''
\subsection{Review 5 (Reviewer F)}
\paragraph*{\textit{The early segments fail to really discuss the MCTS algorithm.  The abbreviation for this is also found in the abstract and should really be in the introductory paragraph.}}
We have added a subsection in the Introduction that describes the MCTS algorithm much more fully than before.
Have removed the abbreviation for MCTS from the abstract.

``MCTS is a tree search algorithm originally designed by R{\'e}mi Coulom \cite{coulom2007efficient} and the major modification of UCT was defined by Kocsis and Szepesv{\'a}ri \cite{kocsis2006bandit} and improved by Kocsis et al \cite{kocsis2006improved}.

MCTS is a tree search algorithm that in games is typically applied directly to the action space. MCTS requires the ability to simulate action sequences and retrieve at least some form of reward (or lack of) from the results of these simulations. The basic steps for MCTS are:

\begin{enumerate}
\item{\emph{Selection} - Selection is the stage where the algorithm navigates the search tree, selecting optimal nodes(Based on the tree policy) until it reaches a leaf node.}
\item{\emph{Expansion} - Expansion is the stage whereby the leaf node is expanded by adding one of the remaining child states if it is not a terminal node.}
\item{\emph{Simulation} - Simulation is the stage where the algorithm forwards the model until a result is achieved. Their is usually a policy that defines how the simulation is made, with the simplest being random possible moves.}
\item{\emph{Backpropagation} - Backpropagation is the stage where the results of the simulation are propagated up the tree, so that they can influence the selection phase.}
\end{enumerate}

MCTS \cite{browne2012survey} has been applied to a wealth of domains and is one of the primary algorithms in use for GGP \cite{finnsson2008simulation}. Primary advantages are that, when given a sufficient forward model, MCTS doesn't require any strategic knowledge about the game itself in order to play.

Standard MCTS plays best when it is able to search far enough to locate states that provide a reward. MCTS tends to stumble when the time or search depth limit given to it isn't sufficient to allow it to locate any sequence of actions that provides a reward in order to differentiate the root's children \cite{perez2012monte}. When MCTS can't find any single state that contained a reward, all children of the node will contain identical values and the algorithm will be forced to make a random choice.''
\paragraph*{\textit{Section II covering preliminary tests is light on technical details and seem ill placed when you consider the subsequent studies later on in the paper.}}
We have removed this section to make way for more detailed results
\paragraph*{\textit{The third page could do with being structured better.  The charts are ill-placed, do not help the flow of the authors argument and need better captions.}}
We have made efforts to improve the layout of the entire paper.
\paragraph*{\textit{The paper would benefit from showing the actual levels used as part of the testing.  Given it makes it harder to understand the impact of later levels.  Figure 10 should be shown much earlier in the paper.}}
The description of each level has had an image of the initial starting state added, as well as being renamed. What was once Figure 10 has been removed due to that image now appearing earlier.

\paragraph*{\textit{The selection of controller types does strike me as odd.  With a random selected and a Variable MAGA that is introduced to resolve shortcoming of the other.  What about a simple 1+1 ES without the macro's?  Or the likes of an A* bot?  Could these not be implemented?}}
A simple 1+1 ES would not be able to find a good solution within the time limits of real time video games. Macro Actions has been proven to vastly improve the ability of GA's to solve complex real time problems such as in Perez et al \cite{perez2013rolling}. A* was considered to have too high a branching factor in this problem but was decided to be investigated in future work.
\paragraph*{\textit{More than once the idea of a language through which to communicate is discussed, but it has no real impact on this paper and should really be saved for when it is explored}}
This has been removed.

### 2015-08-06 Report/ceec.tex
Finished loads

\section{Introduction}
This research problem that this paper will asses is how \gls{ggp} agents perform when trying to solve a simple co-operative problem, with a focus on \gls{mcts}.

@@

Creating \gls{ggp} agents that can co-operate with other players would open the door for more flexible agents in games that can work together with human players. This experiment tests how well current techniques can cope without specifically co-operating with each other. Agents that communicate slowly using a form of Natural Language, should in theory be able to work with human players equally well as they do with other Agents.

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=\linewidth]{scores-allmaps}
\caption{Average score of each AI Agent over all the Maps}
\label{avgScoreAllMaps}
\end{figure}

\begin{figure}[!ht]
\centering
\includegraphics[width=\linewidth]{ticks-allmaps}
\caption{Average Ticks taken for each AI Agent over all the Maps}
\label{avgTicksAllMaps}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\includegraphics[scale=0.5]{level5}
\caption{The initial starting state for \emph{SideBySide}}
\label{Level5State}
\end{figure}

\begin{figure}[!ht]
\centering
\includegraphics[width = \linewidth]{level5-txt-scores}
\caption{Average Score for each AI Agent over \emph{SideBySide}}
\label{avgScoreMap5}
\end{figure}

Level 5 - shown in Figure \ref{Level5State} - poses a particular problem for many of the agents (see Figure \ref{avgScoreMap5}). The asymmetric nature of the level, and the delayed reward caused great difficulty for the Agents. Relying on two button presses and the other agent to get through the open doors - in order - greatly reduced performance. The top agent, \emph{High MCTS}, only managed an average score of $0.44$ compared to its total average of just over $0.8$.

>>>>

\section{Introduction}
This research problem that this paper will asses is how \gls{ggp} agents perform when trying to solve a simple co-operative problem without co-operative abilities, with a focus on \gls{mcts}.

@@

Creating \gls{ggp} agents that can co-operate with other players would open the door for more flexible agents in games that can work together with human players. This experiment tests how well current techniques can cope without specifically co-operating with each other.

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=\linewidth]{scores-allmaps}
\caption{Average score of each AI Agent over all pairings over all the Maps}
\label{avgScoreAllMaps}
\end{figure}

\begin{figure}[!ht]
\centering
\includegraphics[width=\linewidth]{ticks-allmaps}
\caption{Average Ticks taken for each AI Agent over all pairings over all the Maps}
\label{avgTicksAllMaps}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width = \linewidth]{level5-txt-scores}
\caption{Average Score for each AI Agent paired with itself over \emph{Airlock}}
\label{avgScoreMap5}
\end{figure}

Level 5 - shown in Figure \ref{Airlock} - poses a particular problem for many of the agents (see Figure \ref{avgScoreMap5}). The asymmetric nature of the level, and the delayed reward caused great difficulty for the Agents. Relying on two button presses and the other agent to get through the open doors - in order - greatly reduced performance. The top agent, \emph{High MCTS}, only managed an average score of $0.44$ compared to its total average of just over $0.8$.
